Impact of grids and dynamical cores in CESM2.2 on the surface mass balance of the Greenland Ice Sheet

### 2022-05-05 arcticgrids.tex
mods

In addition to summer temperatures, shortwave radiation is an important determinant of snow and ice melt. Figure~\ref{fig:FSDS} shows the summer incident shortwave radiation bias at the surface over Greenland and surrounding seas. The middle panel shows the bias relative to the CERES dataset, and the bottom panel relative to the RACMO2.3p2 dataset. The halo of excessive incident shortwave radiation around the coasts of Greenland is apparent for both datasets in relation to the coarser grids, consistent with the shortwave cloud forcing biases in Figure~\ref{fig:SWCF}.

The ice sheet interior receives too little shortwave radiation in the coarser grids. On the VR grids, both the interior shortwave deficit and the excessive shortwave around the ocean perimeter are improved. This suggests that the coarse-grid clouds are too thick in the Greenland interior and too thin around the perimeter. This is consistent with the total summer cloud fraction bias, computed from the CALIPSO cloud dataset and shown in the top panel of Figure~\ref{fig:FSDS}. Note that total cloud fraction characterizes the cloud field at all vertical levels, and attenuates the changes arising from any single layer due to the occurrence of overlapping clouds at other levels. Despite the attenuated signal, the cloud fractions are too high in the interior and and too low around the oceanic perimeter in the coarser grids, whereas the VR grids have an overall improvement in total cloud fraction bias.

>>>>

In addition to summer temperatures, shortwave radiation is an important determinant of snow and ice melt. Figure~\ref{fig:FSDS} shows the summer incident shortwave radiation bias at the surface over Greenland and surrounding seas. The top panel shows the bias relative to the RACMO2.3p2 dataset, and the middle panel relative to the CERES dataset. The halo of excessive incident shortwave radiation around the coasts of Greenland is apparent for both datasets in relation to the coarser grids, consistent with the shortwave cloud forcing biases in Figure~\ref{fig:SWCF}.

The ice sheet interior receives too little shortwave radiation in the coarser grids. On the VR grids, both the interior shortwave deficit and the excessive shortwave around the ocean perimeter are improved. This suggests that the coarse-grid clouds are too thick in the Greenland interior and too thin around the perimeter. This is consistent with the total summer cloud fraction bias, computed from the CALIPSO cloud dataset and shown in the bottom panel of Figure~\ref{fig:FSDS}. Note that total cloud fraction characterizes the cloud field at all vertical levels, and attenuates the changes arising from any single layer due to the occurrence of overlapping clouds at other levels. Despite the attenuated signal, the cloud fractions are too high in the interior and and too low around the oceanic perimeter in the coarser grids, whereas the VR grids have an overall improvement in total cloud fraction bias.
